Imputation of Incomplete Multilevel Data with \pkg{mice}

### 2021-12-16 Manuscript/Manuscript.Rmd

```{r patterns, fig.height=4, fig.width=3.2, fig.cap = "Missingness in multilevel data", echo=FALSE}
plot_md_set()
# TODO: add border/line
# TODO: remove unit
# TODO: add accolade

The process of analyzing multilevel data is further complicated when not all observations are observed. Just as with single level data, missingness may occur at the unit level. But with multiple levels of data comes the potential for clustered missingness. Missingness in multilevel data can therefore be categorized into two general patterns: systematic missingness and sporadic missingness, see @resc13. We have visualized the difference between these types of missingness in Figure 1. The figure shows an $n \times p$ set $\mathbf{X} = X_1, \dots, X_p$, with $n=5$ units and $p=3$ columns distributed over 3 clusters. Column `X1` is completely observed. Column `X2` is systematically missing and column `X3` is sporadically missing.^[Explain why. GV: niet nodig]

@@

$$
\begin{matrix} 
                          &X1     & X2          & X3            \\
   \hline
   \mathrm{cluster 1}\{ \ &x_{11} &x_{12}       &\mathtt{NA}    \\
                             \ &x_{21}  &x_{22}       &x_{32}         \\
   \mathrm{cluster 2}\{  &x_{31} &\mathtt{NA}  &x_{33}         \\
                          &x_{41} &\mathtt{NA}  &\mathtt{NA}    \\
   \mathrm{cluster 3}\{  &x_{51} &x_{52}       &x_{53}         \\
\end{matrix} 
$$
[GV Ik vind de latex tabel niet tof. ]

>>>>

```{r patterns, fig.height=3, fig.width=4.1, fig.cap = "Missingness in multilevel data", echo=FALSE}
plot_md_set()
```

The process of analyzing multilevel data is further complicated when not all observations are observed. Just as with single level data, missingness may occur at the unit level. But with multiple levels of data comes the potential for clustered missingness. Missingness in multilevel data can therefore be categorized into two general patterns: systematic missingness and sporadic missingness, see @resc13. We have visualized the difference between these types of missingness in Figure 1. The figure shows an $n \times p$ set $\mathbf{X} = X_1, \dots, X_p$, with $n=5$ units and $p=3$ columns distributed over 3 clusters. Column `X1` is completely observed. Column `X2` is systematically missing and column `X3` is sporadically missing.^[Explain why. GV: not necessary]

@@
